\chapter{Related Work}

A few approximation techniques for the graph clustering problem that inspired our approach will be discussed in this chapter.

\section{Spectral Graph Clustering}

\input{report/literature/spectral}


\newpage
\section{Graph Embedding}

Graph embedding falls into four different categories \cite{cai2018comprehensive}: \emph{node embedding}, \emph{edge embedding}, \emph{hybrid embedding} and \emph{whole graph embedding}. Nodes, edges or graph are typically represented by a point in Euclidean space. In this section, we will focus on node embedding and hybrid embedding only.

\subsection{Node Embedding}

In \emph{node embedding}, each node is represented as a vector in a small $d$-dimensional Euclidean space. The common proximity measures are Euclidean norm or inner product.


\subsubsection{Matrix Factorization}

\input{report/literature/matrixfactorization}

\newpage
\subsubsection{Random-walk-based and SkipGram}

\input{report/literature/skipgram}


\newpage
\subsubsection{Neural Network}

\input{report/literature/neuralnetwork}

\newpage
\subsection{Hybrid Embedding}

\input{report/literature/come}

\newpage
\section{Dynamic Graph Clustering}

With regard to Dynamic Graph Clustering, Giulio Rossetti et al \cite{rossetti2018community} published a comprehensive survey on techniques have been used. They classified operations in dynamic graph clustering evolution are as follow:

\begin{itemize}
    \item Birth (New): First appearance of a cluster.
    \item Death: The vanishing of a cluster.
    \item Merge (Join): Two or more clusters merge into one.
    \item Split: One cluster splits into two or more components.
    \item Resurgence: A community vanishes for a short period and comes back.
    \item Grow: A cluster accepts nodes.
    \item Contraction: A cluster rejects nodes.
    \item Continue: A cluster remains unchanged.
\end{itemize}

\newpage
\section{Relation to our work}

\input{report/literature/relation}

